Hand picking similar behaving group of customers to check clustering results - Algorithm 3

### 2021-08-18 supplementary/handpick_algo3.Rmd
adding readme for algo 4

---
title: "Hand picking similar behaving group of customers to check clustering results"
output: pdf_document
---

@@

data_heatmap %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`), size = 0.7) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)")
```
```{r}
#data_pick <- data_pick %>% filter(!(customer_id %in% c(8485375, 8952846)))
library(gracsr)
v2 <- suppressWarnings(scaled_dist_gran(data_pick, "hour_day", response = "general_supply_kwh", quantile_prob_val = c(0.5, 0.75, 0.9))) %>% rename("dist_hod" = "dist")
v3 <- suppressWarnings(scaled_dist_gran(data_pick, "day_month", response = "general_supply_kwh", quantile_prob_val = c(0.5, 0.75, 0.9))) %>% rename("dist_dom" = "dist")
data_dist <- v3 %>% left_join(v2) %>% mutate(dist = dist_hod) %>% 
    pivot_wider(-c(3, 4), names_from = customer_to,
              values_from = dist) %>%
  rename("customer_id" = "customer_from")

d = stats::as.dist(data_dist[,-1])
hc = stats::hclust(d,method="complete")

groups <- tibble(group = cutree(hc, k=3), customer_id = data_dist$customer_id)
groups
groups %>% filter(group==2)
groups %>% filter(group==3)
groups %>% group_by(group) %>% summarise(n=n())
```

>>>>

---
title: "Hand picking similar behaving group of customers to check clustering results - Algorithm 3"
output: pdf_document
---

@@

data_heatmap %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`), size = 0.7) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)")
```
```{r,echo = TRUE}
#data_pick <- data_pick %>% filter(!(customer_id %in% c(8485375, 8952846)))
library(gracsr)
v2 <- suppressWarnings(
  scaled_dist_gran(data_pick, "hour_day", 
                   response = "general_supply_kwh",
                   quantile_prob_val = c(0.5, 0.75, 0.9))) %>% rename("dist_hod" = "dist")
v3 <- suppressWarnings(
  scaled_dist_gran(data_pick, "day_month",
                   response = "general_supply_kwh", 
                   quantile_prob_val = c(0.5, 0.75, 0.9))) %>% rename("dist_dom" = "dist")

data_dist <- v3 %>% 
  left_join(v2) %>%
  mutate(dist = dist_dom) %>% 
    pivot_wider(-c(3, 4), 
                names_from = customer_to,
              values_from = dist) %>%
  rename("customer_id" = "customer_from")
```

```{r}
d = stats::as.dist(data_dist[,-1])
hc = stats::hclust(d,method="complete")

groups <- tibble(group = cutree(hc, k=3), customer_id = data_dist$customer_id)
groups %>% group_by(group) %>% summarise(n=n())
groups %>% filter(group==1)
groups %>% filter(group==2)
groups %>% filter(group==3)
```
